All Your Graphs Belong to Us

### 2012-07-20 doc/asplos13/implementation.tex
Change uses of gasnet to \gasnet; remove redundant ack from method.tex:Systems

Underneath the aggregation layer, Grappa uses the GASNet communication
library \TODO{cite GASNet} to actually move data. All interprocess
communication, whether on or off a cluster node, is handled by the
GASNet library. GASNet is able to take advantage of many communication
mechanisms, including Ethernet and Infiniband between nodes, as well as
shared memory within a node.

>>>>

Underneath the aggregation layer, Grappa uses the \gasnet~communication
library \TODO{cite GASNet} to actually move data. All interprocess
communication, whether on or off a cluster node, is handled by the
\gasnet~library. \gasnet~is able to take advantage of many communication
mechanisms, including Ethernet and Infiniband between nodes, as well as
shared memory within a node.

### 2012-07-20 doc/asplos13/method.tex
Change uses of gasnet to \gasnet; remove redundant ack from method.tex:Systems

\subsection{Systems}
For measurements, we run Grappa on a 144-node cluster of AMD
Interlagos processors, located at Pacific Northwest National Lab
(PNNL). Nodes have 32 core (every pair share a floating-point
unit) 2.1-GHz processors, and 64GB of memory, and \TODO{xxx 40Gb network card}. \TODO{cluster
    uses xxx Infiniband switch}. We configure the nodes to have 32 1-GB
hugepages to minimize TLB misses for the random access patterns we
expect from irregular applications. The results we present are for
this machine, but we have also run Grappa on our own 12-node Intel
Xeon Westmere cluster.

For the MTA comparison, we use a 128-node Cray XMT (3rd generation
of the MTA), also located at PNNL. Each node consists of a 500-MHz MTA Threadstorm multithreaded
processor that supports 128 streams. The machine uses Cray's proprietary
SeaStar2 interconnection network.

>>>>

\subsection{Systems}
For measurements, we run Grappa on a 144-node cluster of AMD
Interlagos processors. Nodes have 32-core (every pair share a floating-point
unit) 2.1-GHz processors, 64GB of memory, and \TODO{xxx 40Gb network card}. \TODO{cluster
    uses xxx Infiniband switch}. We configure the nodes to have 32 1-GB
hugepages to minimize TLB misses for the random access patterns we
expect from irregular applications. The results we present are for
this machine, but we have also run Grappa on our own 12-node Intel
Xeon Westmere cluster.

We compare to the MTA using a 128-node Cray XMT (3rd generation MTA). 
Each node consists of a 500-MHz MTA Threadstorm multithreaded
processor that supports 128 streams. The machine uses Cray's proprietary
SeaStar2 interconnection network.
